BMI-manuscript

### 2020-10-26 manuscript/manuscript.Rmd
impliminting quantreg

---
title: "BMI-manuscript"
output: 
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
---
\section{introduction}
Body Mass Idex (BMI) playes an important rule in predicting heart disease risk. BMI     
 .
[@van2012estimating]
\section{methode}
From the figure we see ...

>>>>

---
title: "BMI-manuscript"
output: 
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
---
\section{introduction}

Body Mass Idex (BMI) playes an important rule in predicting heart disease risk.      
 .
[@van2012estimating]
\section{methode}
We used Bayesian hierarchical logistic regression (12) with random intercepts by calendar year to estimate diabetes
prevalence and incidence as a function
of age (18 – 84 years in 1-year
intervals), race/ethnicity (non-Hispanic
white, non-Hispanic black, Hispanic, or
other), sex, and BMI (underweight,
 18.5 kg/m2; normal weight, 18.5 to
 25 kg/m2; overweight, 25 to 30 kg/
m2; obese, 30 to 35 kg/m2; and very
From the figure we see

### 2020-10-26 manuscript/manuscript.tex
impliminting quantreg

Body Mass Idex (BMI) playes an important rule in predicting heart
disease risk. BMI\\
. (Van de Kassteele et al. 2012) \section{methode} From the figure we
see \ldots{}

>>>>

Body Mass Idex (BMI) playes an important rule in predicting heart
disease risk.\\
. (Van de Kassteele et al. 2012) \section{methode} We used Bayesian
hierarchical logistic regression (12) with random intercepts by calendar
year to estimate diabetes prevalence and incidence as a function of age
(18 -- 84 years in 1-year intervals), race/ethnicity (non-Hispanic
white, non-Hispanic black, Hispanic, or other), sex, and BMI
(underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight,
25 to 30 kg/ m2; obese, 30 to 35 kg/m2; and very From the figure we see
